\exercisesheader{}

% 33

\eoce{\qt{Increasing corn yield\label{increase_corn_yield}} A large farm wants to 
try out a new type of fertilizer to evaluate whether it will improve the 
farm's corn production. The land is broken into plots that produce an 
average of 1,215 pounds of corn with a standard deviation of 94 pounds per 
plot. The owner is interested in detecting any average difference of at 
least 40 pounds per plot. How many plots of land would be needed for the 
experiment if the desired power level is 90\%?
Use $\alpha = 0.05$.
Assume each plot of land gets 
treated with either the current fertilizer or the new fertilizer.
}{}

% 34

\eoce{\qt{Email outreach efforts\label{email_outreach_efforts}} A medical research 
group is recruiting people to complete short surveys about their medical 
history. For example, one survey asks for information on a person's family 
history in regards to cancer. Another survey asks about what topics were 
discussed during the person's last visit to a hospital. So far, as people 
sign up, they complete an average of just 4~surveys, and the standard 
deviation of the number of surveys is about~2.2. The research group wants to 
try a new interface that they think will encourage new enrollees to complete 
more surveys, where they will randomize each enrollee to either get the new 
interface or the current interface. How many new enrollees do they need for 
each interface to detect an effect size of 0.5 surveys per enrollee, if the 
desired power level is 80\%?
Use $\alpha = 0.05$.
}{}
