\exercisesheader{}

% 31

\eoce{\qt{Customers at a coffee shop\label{coffee_shop_customers}} A coffee shop 
serves an average of 75 customers per hour during the morning rush.
\begin{parts}
\item
  Which distribution have we studied that is most appropriate
  for calculating the probability of a given number of customers
  arriving within one hour 
  during this time of day?
\item What are the mean and the standard deviation of the number of customers 
this coffee shop serves in one hour during this time of day?
\item Would it be considered unusually low if only 60 customers showed up to 
this coffee shop in one hour during this time of day?
\item Calculate the probability that this coffee shop serves 70 customers in 
one hour during this time of day.
\end{parts}
}{}

% 32

\eoce{\qt{Stenographer's typos\label{stenographer_typos}} A very skilled 
court stenographer makes one typographical error (typo) per hour on average.
\begin{parts}
\item What probability distribution is most appropriate for calculating the 
probability of a given number of typos this stenographer makes in an hour?
\item What are the mean and the standard deviation of the number of typos 
this stenographer makes?
\item Would it be considered unusual if this stenographer made 4 typos in a 
given hour? 
\item Calculate the probability that this stenographer makes at most 2 typos 
in a given hour.
\end{parts}
}{}

% 33

\eoce{\qtq{How many cars show up\label{cars_in_parking_lot}}
For Monday through Thursday when there isn't a holiday,
the average number of vehicles that visit a particular
retailer between 2pm and 3pm each afternoon is 6.5,
and the number of cars that show up on any given day
follows a Poisson distribution.
\begin{parts}
\item
    What is the probability that exactly
    5 cars will show up next Monday?
\item
    What is the probability that
    0, 1, or 2 cars will show up next Monday
    between 2pm and 3pm?
\item
    There is an average of 11.7 people who visit during
    those same hours from vehicles.
    Is it likely that the number of people visiting
    by car during this hour is also Poisson?
    Explain.
\end{parts}
}{}

% 34

\eoce{\qt{Lost baggage\label{lost_baggage}}
Occasionally an airline will lose a bag.
Suppose a small airline has found it can reasonably
model the number of bags lost each weekday using a
Poisson model with a mean of 2.2 bags.
\begin{parts}
\item
    What is the probability that the airline
    will lose no bags next Monday?
\item
    What is the probability that the airline
    will lose 0, 1, or 2 bags on next Monday?
\item
    Suppose the airline expands over the course
    of the next 3 years, doubling the number of
    flights it makes, and the CEO asks you if
    it's reasonable for them to continue
    using the Poisson model with a mean of~2.2.
    What is an appropriate recommendation?
    Explain.
\end{parts}
}{}
