\reviewexercisesheader{}

% 35

\eoce{\qt{Roulette winnings\label{roulette_winnings}} In the game of roulette, a 
wheel is spun and you place bets on where it will stop. One popular bet is 
that it will stop on a red slot; such a bet has an 18/38 chance of winning. 
If it stops on red, you double the money you bet. If not, you lose the money 
you bet. Suppose you play 3 times, each time with a \$1 bet. Let Y represent 
the total amount won or lost. Write a probability model for Y.
}{}

% 36

\eoce{\qt{Speeding on the I-5, Part I\label{speeding_i5_intro}} The distribution of 
passenger vehicle speeds traveling on the Interstate 5 Freeway (I-5) in 
California is nearly normal with a mean of 72.6 miles/hour and a standard 
deviation of 4.78 miles/hour.\footfullcite{Johnson+Murray:2010}
\begin{parts}
\item What percent of passenger vehicles travel slower than 80 miles/hour?
\item What percent of passenger vehicles travel between 60 and 80 miles/hour?
\item How fast do the fastest 5\% of passenger vehicles travel?
\item The speed limit on this stretch of the I-5 is 70 miles/hour. 
Approximate what percentage of the passenger vehicles travel above the speed 
limit on this stretch of the I-5.
\end{parts}
}{}

% 37

\eoce{\qt{University admissions\label{university_admissions}} Suppose a university 
announced that it admitted 2,500 students for the following year's freshman 
class. However, the university has dorm room spots for only 1,786 freshman 
students. If there is a 70\% chance that an admitted student will decide to 
accept the offer and attend this university, what is the approximate 
probability that the university will not have enough dormitory room spots for 
the freshman class?
}{}

% 38

\eoce{\qt{Speeding on the I-5, Part II\label{speeding_i5_geometric}} 
Exercise~\ref{speeding_i5_intro} states that the distribution of speeds of 
cars traveling on the Interstate 5 Freeway (I-5) in California is nearly 
normal with a mean of 72.6 miles/hour and a standard deviation of 4.78 
miles/hour. The speed limit on this stretch of the I-5 is 70 miles/hour.
\begin{parts}
\item A highway patrol officer is hidden on the side of the freeway. What is 
the probability that 5~cars pass and none are speeding? Assume that the 
speeds of the cars are independent of each other.
\item On average, how many cars would the highway patrol officer expect to 
watch until the first car that is speeding? What is the standard deviation of 
the number of cars he would expect to watch?
\end{parts}
}{}

% 39

\eoce{\qt{Auto insurance premiums\label{auto_insurance_premiums}} Suppose a 
newspaper article states that the distribution of auto insurance premiums for 
residents of California is approximately normal with a mean of \$1,650. The 
article also states that 25\% of California residents pay more than \$1,800. 
\begin{parts}
\item What is the Z-score that corresponds to the top 25\% (or the $75^{th}$ 
percentile) of the standard normal distribution?
\item What is the mean insurance cost? What is the cutoff for the 75th 
percentile?
\item Identify the standard deviation of insurance premiums in California.
\end{parts}
}{}

% 40

\eoce{\qt{SAT scores\label{sat_scores}}
SAT scores (out of 1600) are distributed 
normally with a mean of 1100 and a standard deviation of 200.
Suppose a school council awards a certificate of excellence
to all students who score at least 1350 on the SAT,
and suppose we pick one of the recognized students at random.
What is the probability this student's score will be
at least 1500?
(The material covered in
Section~\ref{conditionalProbabilitySection}
on conditional probability
would be useful for this question.)
}{}

% 41

\eoce{\qt{Married women} \label{married_women} The American Community Survey 
estimates that 47.1\% of women ages 15 years and over are married.
\footfullcite{marWomenACS}
\begin{parts}
\item We randomly select three women between these ages. What is the 
probability that the third woman selected is the only one who is married?
\item What is the probability that all three randomly selected women are 
married?
\item On average, how many women would you expect to sample before selecting 
a married woman? What is the standard deviation?
\item If the proportion of married women was actually 30\%, how many women 
would you expect to sample before selecting a married woman? What is the 
standard deviation?
\item Based on your answers to parts (c) and (d), how does decreasing the 
probability of an event affect the mean and standard deviation of the wait 
time until success?
\end{parts}
}{}

\D{\newpage}

% 42

\eoce{\qt{Survey response rate\label{survey_response_rate}} Pew Research reported 
that the typical response rate to their surveys is only 9\%. If for a 
particular survey 15,000 households are contacted, what is the probability 
that at least 1,500 will agree to respond? \footfullcite{surveysPew}
}{}

% 43

\eoce{\qt{Overweight baggage\label{overweight_baggage}} Suppose weights of the 
checked baggage of airline passengers follow a nearly normal distribution 
with mean 45 pounds and standard deviation 3.2 pounds. Most airlines charge a 
fee for baggage that weigh in excess of 50 pounds. Determine what percent of 
airline passengers incur this fee.
}{}

% 44

\eoce{\qt{Heights of 10 year olds, Part I\label{heights_10_yrs}}
Heights of 10 year olds, regardless of gender, closely follow
a normal distribution with mean 55 inches and standard deviation
6~inches.
\begin{parts}
\item
    What is the probability that a randomly chosen 10 year old
    is shorter than 48 inches?
\item
    What is the probability that a randomly chosen 10 year old
    is between 60 and 65 inches?
\item
    If the tallest 10\% of the class is considered
    ``very tall'',
    what is the height cutoff for ``very tall"?
\end{parts}
}{}

% 45

\eoce{\qt{Buying books on Ebay\label{buy_boooks_ebay}}
Suppose you're considering buying your expensive chemistry
textbook on Ebay.
Looking at past auctions suggests that the 
prices of this textbook follow an approximately normal
distribution with mean \$89 and standard deviation \$15.
\begin{parts}

\item What is the probability that a randomly selected auction for this book 
closes at more than \$100?

\item Ebay allows you to set your maximum bid price so that if someone 
outbids you on an auction you can automatically outbid them, up to the 
maximum bid price you set. If you are only bidding on one auction, what are 
the advantages and disadvantages of setting a bid price too high or too low? 
What if you are bidding on multiple auctions?

\item If you watched 10 auctions, roughly what percentile might you use for a 
maximum bid cutoff to be somewhat sure that you will win one of these ten 
auctions? Is it possible to find a cutoff point that will ensure that you win 
an auction?

\item If you are willing to track up to ten auctions closely, about what 
price might you use as your maximum bid price if you want to be somewhat sure 
that you will buy one of these ten books?

\end{parts}
}{}

% 46

\eoce{\qt{Heights of 10 year olds, Part II\label{heights_10_yrs_prob}}
Heights of 10 year olds, regardless of gender, closely follow
a normal distribution with mean 55 inches and standard deviation
6~inches.
\begin{parts}
\item
    The height requirement for \textit{Batman the Ride} at
    Six Flags Magic Mountain is 54 inches.
    What percent of 10 year olds cannot go on this ride?
\item
    Suppose there are four 10 year olds.
    What is the chance that at least two of them
    will be able to ride \emph{Batman the Ride}?
\item
    Suppose you work at the park to help them better
    understand their customers' demographics, and
    you are counting people as they enter
    the park.
    What is the chance that the first 10 year old
    you see who can ride \emph{Batman the Ride} is
    the 3rd 10 year old who enters the park?
\item
    What is the chance that the fifth 10 year old
    you see who can ride \emph{Batman the Ride} is
    the 12th 10 year old who enters the park?
\end{parts}
}{}

% 47

\eoce{\qt{Heights of 10 year olds, Part III\label{heights_10_yrs_dist}}
Heights of 10 year olds, regardless of gender, closely follow
a normal distribution with mean 55 inches and standard deviation
6~inches.
\begin{parts}
\item
    What fraction of 10 year olds are taller than
    76 inches?
\item\label{heights_10_yrs_dist_76_inches}
    If there are 2,000 10 year olds entering
    Six Flags Magic Mountain in a single day,
    then compute the expected number of
    10 year olds who are at least 76 inches tall.
    (You may assume the heights of the 10-year olds
    are independent.)
\item
    Using the binomial distribution,
    compute the probability that 0 of the 2,000
    10 year olds will be at least 76 inches tall.
\item
    The number of 10 year olds who enter
    Six Flags Magic Mountain and are
    at least 76 inches tall in a given day
    follows a Poisson distribution with
    mean equal to the value found in
    part~(\ref{heights_10_yrs_dist_76_inches}).
    Use the Poisson distribution to identify
    the probability no 10 year old will enter
    the park who is 76 inches or taller.
\end{parts}
}{}

% 48

\eoce{\qt{Multiple choice quiz\label{mc_quiz}} In a multiple choice quiz there are 
5 questions and 4 choices for each question (a, b, c, d). Robin has not 
studied for the quiz at all, and decides to randomly guess the answers. What 
is the probability that
\begin{parts}
\item the first question she gets right is the $3^{rd}$ question?
\item she gets exactly 3 or exactly 4 questions right?
\item she gets the majority of the questions right?
\end{parts}
}{}
